### 2015-02-20 fundamentals/impl.tex
another unnecessary sentence

Verification may be defined as the question, ``Is \Cyclus being built correctly?''
To answer this question, \Cyclsu relies on software development best practices
such as testing,
documentation, version control, style guidelines, and continuous integration.
This suite of process controls supplies mechanism for reliable and reproducible
software. The impetus to implement these controls correctly is particularly strong in a scientific
context because of the emphasis on reproducibility and provenance. These verification techniques are
discussed individually in the sections that follow.

>>>>

Verification may be defined as the question, ``Is \Cyclus being built correctly?''
To answer this question, \Cyclus relies on software development best practices
such as testing,
documentation, version control, style guidelines, and continuous integration to
ensure reliability and reproducibility. These verification techniques are
discussed individually in the sections that follow.
